A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)

### 2018-04-12 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

{\it Upscaling} is a term commonly used in the oil and gas sector and is often referred, throughout the applied mathematics and engineering communities, as a form of model order reduction (or reduced order models, MOR/ROM). Depending on the context in which MOR is used, it can simply be referred as dimensionality reduction. The definition of MOR also depends on the context it is being used, but it suffices to state that MOR captures the essential features of a system, structure or parameter \cite{Schilders2008}. This implies that an original system exists with more detailed information. Figure~\ref{fig:IllustrationMOR} presents a graphical intepretation of the MOR concept in which it shows that even with the reduced number of facets, the graphic on the rhs of this illustration is recognised as that of a rabbit.

>>>>

{\it Upscaling} is a term commonly used in the oil and gas sector and is often referred, throughout the applied mathematics and engineering communities, as a form of model order reduction (or reduced order models, MOR/ROM). Depending on the context in which MOR is used, it can simply be referred as dimensionality reduction. The definition of MOR also depends on the context it is being used, but it suffices to state that MOR captures the essential features of a system, structure or parameter \cite{Schilders2008}. This implies that an original system exists with more detailed information. Figure~\ref{fig:IllustrationMOR} presents an interpretation of MOR concept in which a graphical representation of a rabbit is reconstructed with a reduced number of facets (rhs of this illustration).

### 2018-04-12 Papers/AppliedMaths2018/article_figure1.tex
updates

%%%%
%%%%  FIGURE
%%%%
%\begin{landscape}
\begin{figure}[ht] 
\vbox{\vspace{-1cm}
\centering
\includegraphics[width=.56\textwidth]{./Pics/Introduction/Graphical-illustration-of-model-order-reduction.png}
\vspace{0.cm}
\vspace{0.5cm}
}   
\caption{Graphical Illustration of model order reduction (Initially used by \citet{Schilders2008}, with graphics credited to Harvard University, Microsoft Research)}
\vspace{1.5cm}
\label{fig:IllustrationMOR}
\end{figure}

>>>>

%%%%
%%%%  FIGURE
%%%%
%\begin{landscape}
\begin{figure}[ht] 
\vbox{\vspace{-1cm}
\centering
\includegraphics[width=.56\textwidth]{./Pics/Introduction/Graphical-illustration-of-model-order-reduction.png}
\vspace{0.cm}
\vspace{0.5cm}
}   
\caption{Graphical illustration of model order reduction (initially used by \citet{Schilders2008}, with graphics credited to Harvard University, Microsoft Research.)}
\vspace{1.5cm}
\label{fig:IllustrationMOR}
\end{figure}
